%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\definecolor{accent}{HTML}{4B3F72}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\color{accent}\scshape\raggedright\large
}{}{0em}{}[\color{accent}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape \color{accent} Makayla Choudary} \\ \vspace{1pt}
    \small \href{mailto:mgc9912@nyu.edu}{\underline{mgc9912@nyu.edu}} $|$ 
    \href{https://linkedin.com/in/makayla-choudary}{\underline{linkedin.com/in/makayla-choudary}} $|$
    \href{https://github.com/makayla-chou}{\underline{github.com/makayla-chou}}
     $|$
    \href{https://makayla-chou.github.io/personal_website/}{\underline{personal website}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {New York University}{New York, New York}
      {Bachelor of Science in Computer Engineering}{Expected Graduation: May 2027}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures, Computer Architecture, Machine Learning, Digital Logic, Circuits, Linear Algebra, Statistics}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Analytics Intern}{Summer 2025}
      {Travel Resorts of America}{Remote / North Carolina}
      \resumeItemListStart
        \resumeItem{Built and automated Power BI dashboards tracking occupancy, cancellations, and site utilization across multiple resort properties, improving visibility into operational performance.}
        \resumeItem{Designed Excel Power Query transformations and DAX measures to standardize key operational metrics, including unused sites and active reservations.}
        \resumeItem{Developed Python and Databricks workflows using Snowflake datasets to analyze loan delinquency milestones across 30/60/90/120+ day thresholds.}
        \resumeItem{Implemented Collibra Data Quality rules to validate completeness and identify discrepancies across booking, financial, and site-level data sources.}
        \resumeItem{Delivered executive-facing performance reports used to support operational planning, reporting accuracy, and management decision-making.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{CatOps - Agentic Reinforcement Learning Cat Simulator} $|$ \emph{Python, Streamlit, Pandas, Plotly}}{Summer 2026}
      \resumeItemListStart
        \resumeItem{Built an interactive reinforcement learning simulator where virtual cat agents learn action policies using Q-learning across balanced, strict, and chaotic environments.}
        \resumeItem{Developed an agentic decision loop that observes cat states, selects actions from learned Q-values, explains decisions, reflects on outcomes, and stores session memory.}
        \resumeItem{Created Streamlit dashboards to visualize reward trends, action frequencies, scratch behavior, learned policies, and Q-learning performance against a random baseline.}
      \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Predictive Maintenance ML System} $|$ \emph{Python, pandas, scikit-learn, Jupyter, Git/GitHub}}{Summer 2026}
      \resumeItemListStart
        \resumeItem{Built a machine learning pipeline to predict equipment failure risk from industrial sensor data using temperature, torque, rotational speed, and tool wear features.}
        \resumeItem{Addressed severe class imbalance, with failures representing 3.39\% of samples, by prioritizing recall and F2 score over accuracy.}
        \resumeItem{Compared Logistic Regression, Random Forest, and Gradient Boosting models, applying threshold optimization to prioritize failure detection.}
        \resumeItem{Evaluated models using confusion matrices, recall, F2 score, and feature importance to compare failure detection performance.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{LSTM Time-Series Prediction Project} $|$ \emph{Python, pandas, scikit-learn, matplotlib, Jupyter, Git}}{Spring 2025}
      \resumeItemListStart
        \resumeItem{Built and trained an LSTM neural network to model sequential time-series data and forecast future values.}
        \resumeItem{Created preprocessing workflows for data cleaning, normalization, train-test splitting, and sequence generation.}
        \resumeItem{Evaluated model performance using prediction plots and error metrics to compare predicted values against actual trends.}
        \resumeItem{Experimented with architecture depth, sequence length, and hyperparameters to improve forecasting accuracy.}
      \resumeItemListEnd

 

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, C++, Java, SQL \\
     \textbf{Data/ML:} pandas, NumPy, scikit-learn, matplotlib, Power BI, Excel Power Query, DAX \\
     \textbf{Cloud/Data Tools:} Databricks, Snowflake, Collibra Data Quality \\
     \textbf{Hardware/Engineering:} Raspberry Pi, Arduino, GPIO, motor control, digital logic, circuits \\
     \textbf{Developer Tools:} Git, GitHub, Jupyter Notebook
    }}
 \end{itemize}

%-------------------------------------------
\end{document}